---
title: "Post_Event_Report"
author: "Sam Gottuso"
date: "December 7, 2017"
runtime: shiny
output:
  html_document: 
    css: test_css.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(ggplot2)
library(dplyr)
library(knitr)
library(rmarkdown)
library(readr)
library(reshape2)
library(leaflet)
library(zipcode)
library(rgdal)
library(grid)
library(gridExtra)
library(mapview)
library(shiny)




##Current steps for working the report generator

# 1) Import both your cleaned data file, and survey data (All Individual Responses-- XLS+ format)-- ensure that all of the columns are the in the standard format (names/coulmn numbers should match up with column_numbers_adobe or column_numbers_webx)

# 2) Run them through the event cleaner function (at the end of all of the event_meta_data lines) do event_meta_data<-Event_data_cleaner("file format","Name of the event", "Event type", data file, survey data)

#3) change the event_map_data function to run with the most recent version

#4) if desired change the output in the header to be pdf_document

#5) Save as new file and run (knit)




##Load in functions necessary for creating DFs

#Figures out the mode of dates to determine what the correct date is
Mode_manual <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}


#standardization of which columns/names of columns
column_names_adobe<-c("First_name","Last_name","Email","Status","Login","Logoff","Duration","Role","Role_other","Organization_name","ID","Region","Zip")
  
column_numbers_adobe<-c(3,4,5,7,8,9,10,12,13,16,20,22,24)

column_names_webx<-column_names_adobe
column_numbers_webx<-c(1,2,3,10,11,12,19,33,34,37,43,41,51)

column_numbers_sm<-seq(10,18)
column_names_sm<-c("Track","Reported_role","Reported_role_other","Valuable_use_time","Connect_others","Take_action","Enhanced_knowledge","Suggestions","Technical_difficulties")



##Test data


#PIA2

PIA_2_first_import<-read_excel(path='PIA2_analysis.xlsx',sheet = 2)


PIA_2_survey_first_import<-read_excel(path='PIA_2_survey.xlsx',sheet = 1)



#ecqm_HIT_Review

eCQM_HIT_first_import<-read_excel(path='eCQM_HIT_analysis.xlsx',sheet = 1)

ecqm_HIT_survey<-read_excel(path='eCQM_HIT_Survey.xlsx', sheet = 1)

#what you need to know about financial reporting

need_to_know_first_import<-read_excel(path='need_to_know_analysis.xlsx',sheet = 1) 

need_to_know_survey<-read_excel(path='need_to_know_survey.xlsx',sheet = 1)


#PIA3

PIA_3_first_import<-read_excel(path='PIA3_analysis.xlsx',sheet = 2)


PIA_3_survey_first_import<-read_excel(path='PIA_3_survey.xlsx',sheet = 1)


#PIA4

PIA_4_first_import<-read_excel(path='PIA4_BHI_CM_analysis.xlsx',sheet = 2)


PIA_4_survey_first_import<-read_excel(path='PIA4_BHI_CM_Survey.xlsx',sheet = 1)


#PIA5

PIA_5_first_import<-read_excel(path='PIA5_BHI_Behaviorist_analysis.xlsx',sheet = 1)

PIA_5_survey_first_import<-read_excel(path='PIA5_BHI_Behaviorist_Survey.xlsx',sheet = 1)

#Taking the Next Step Webinar

Taking_next_step_first_import<-read_excel(path='taking_next_step_analysis.xlsx',sheet = 1)

Taking_next_step_survey_first_import<-read_excel(path='Taking_next_step_Survey.xlsx',sheet = 1)

#PIA6
PIA_6_first_import<-read_excel(path='PIA6_Data_Patients_analysis.xlsx',sheet = 1)

PIA_6_survey_first_import<-read_excel(path='PIA6_Data_Patients_Survey.xlsx',sheet = 1)

#PIA7

PIA_7_first_import<-read_excel(path='PIA7_Data_Specialty_analysis.xlsx',sheet = 1)

PIA_7_survey_first_import<-read_excel(path='PIA7_Data_Specialty_Survey.xlsx',sheet = 1)

#PIA8

PIA_8_first_import<-read_excel(path='PIA8_Share_Care_analysis.xlsx',sheet = 1)

PIA_8_survey_first_import<-read_excel(path='PIA8_Share_Care_Survey.xlsx',sheet = 1)

#Submitting eCQM

submitting_eCQM_first_import<-read_excel(path = 'Submitting_eCQM_analysis.xlsx',sheet = 1)

submitting_eCQM_survey_first_import<-read_excel(path = 'Submitting_eCQM_Survey.xlsx', sheet = 1)

#PIA9

PIA_9_first_import<-read_excel(path = 'PIA9_Timely_Exchange_analysis.xlsx',sheet = 1)
PIA_9_survey_first_import<-read_excel(path = 'PIA9_Timely_Exchange_survey.xlsx',sheet = 1)

#Financial_Reporting

FR_OH_first_import<-read_excel(path='FR_OH_analysis.xlsx',sheet = 1)
FR_OH_survey_first_import<-read_excel(path = 'FR_OH_Survey.xlsx',sheet = 1)

#CDOS_AC
CDOS_AC_first_import<-read_excel(path='CDOS_AC_analysis.xlsx',sheet = 1)
CDOS_AC_survey_first_import<-read_excel(path = 'CDOS_AC_Survey.xlsx',sheet = 1)

#CDOS_CM
CDOS_CM_first_import<-read_excel(path='CDOS_CM_analysis.xlsx',sheet = 1)
CDOS_CM_survey_first_import<-read_excel(path = 'CDOS_CM_Survey.xlsx',sheet = 1)

##Automatically clean and spit out necessary data 

event_meta_data<-data.frame(matrix(NA,ncol=26))
colnames(event_meta_data)<-c("Date","Event_name","Event Type","Attendance","Attendance_rate","Practice_attendees","Administration","Clinicians","Care_managers","Data_analyst","Project_managers","Project_director","Quality_improvement","CMS","Contractors","Payers","Vendors","Unique_practices","Total_practices","Survey_response_rate","Positive_VUT","Neutral_VUT","Negative_VUT","Positive_TA","Netural_TA","Negative_TA")

Event_data_cleaner<-function(type,event_name,event_type,imported_data,imported_survey_data){
  if(type=="adobe"){
    cleaned_data<-imported_data[,column_numbers_adobe]
    colnames(cleaned_data)<-column_names_adobe
  }else if(type=="webx"){
    cleaned_data<-imported_data[,column_numbers_webx]
    colnames(cleaned_data)<-column_names_webx
  }
  
  cleaned_data<-as.data.frame(cleaned_data)
  
  #Adding date
  date<-Mode_manual(na.omit(cleaned_data$Login))

  #Adding Attendance and attendance rate
  attendance<-(sum(cleaned_data$Status=="Attended",na.rm = TRUE))
  attendance_rate<-(attendance)/length(cleaned_data$Status)

  #Adding practice participants-- from attended only
  attended_df<-cleaned_data[(cleaned_data$Status=="Attended"),]
  admin<-sum(attended_df$Role=="Administration",na.rm = TRUE)
  drs<-sum(attended_df$Role=="Clinicians providing healthcare services within context of model",na.rm = TRUE)
  cm<-sum(attended_df$Role=="Care Manager",na.rm = TRUE)
  da<-sum(attended_df$Role=="Data Analyst",na.rm = TRUE)
  pm<-sum(attended_df$Role=="Project Manager/Coordinator",na.rm = TRUE)
  pd<-sum(attended_df$Role=="Project Director/Principal Investigator",na.rm = TRUE)
  qi<-sum(attended_df$Role=="Quality Improvement Director",na.rm = TRUE)
  PA<-sum(admin,drs,cm,da,pm,pd,qi)
  
  #Adding non-practice attendees
  cms<-sum(attended_df$Role=="CMS",na.rm = TRUE)
  cnt<-sum(attended_df$Role=="Contractor",na.rm = TRUE)
  pay<-sum(attended_df$Role_other=="Payer",na.rm = TRUE)
  ven<-sum(attended_df$Role_other=="Vendor",na.rm = TRUE)
  
  #Practices
  up=length(unique(attended_df$ID))
  tp=sum(attended_df$ID!="Not Available",na.rm = TRUE)
  
  
  ##Survey Stuff
  cleaned_data_survey<-imported_survey_data[,column_numbers_sm]
  colnames(cleaned_data_survey)<-column_names_sm
  
  cleaned_data_survey<-tail(cleaned_data_survey,-1)
  cleaned_data_survey<-cleaned_data_survey[rowSums(is.na(cleaned_data_survey))!=ncol(cleaned_data_survey),]
  
  cleaned_data_survey<-as.data.frame(cleaned_data_survey)
  
  srr<-(length(cleaned_data_survey$Track)/attendance)
  
  cleaned_data_survey$VUT<-parse_number(cleaned_data_survey$Valuable_use_time)
  cleaned_data_survey$TA<-parse_number(cleaned_data_survey$Take_action)
  
  p_vut<-sum(cleaned_data_survey$VUT==1)+sum(cleaned_data_survey$VUT==2)
  nu_vut<-sum(cleaned_data_survey$VUT==3)
  n_vut<-sum(cleaned_data_survey$VUT==4)+sum(cleaned_data_survey$VUT==5)
  
  p_TA<-sum(cleaned_data_survey$TA==1)+sum(cleaned_data_survey$TA==2)
  nu_TA<-sum(cleaned_data_survey$TA==3)
  n_TA<-sum(cleaned_data_survey$TA==4)+sum(cleaned_data_survey$TA==5)
  
  
  TD<-sum(cleaned_data_survey$Technical_difficulties=="Yes")
  
  
  
#append it onto the end of our event meta data frame which we will use to create all of graphs. 

append_list<-c(date,event_name,event_type,attendance,attendance_rate,PA,admin,drs,cm,da,pm,pd,qi,cms,cnt,pay,ven,up,tp,srr,p_vut,nu_vut,n_vut,p_TA,nu_TA,n_TA,TD)

event_meta_data<-rbind(event_meta_data,append_list)

return(event_meta_data)
  
}


#Each event has to be appended unto event_meta_data using Event_Data_Cleaner

event_meta_data<-Event_data_cleaner("adobe","PIA2","PIA",PIA_2_first_import,PIA_2_survey_first_import)
event_meta_data<-Event_data_cleaner("webx","eCQM HIT Review","National Webinar",eCQM_HIT_first_import,ecqm_HIT_survey)
event_meta_data<-Event_data_cleaner("webx","What you need to know Financial Reporting","National Webinar",need_to_know_first_import,need_to_know_survey)
event_meta_data<-Event_data_cleaner("adobe","PIA 3: Risk Stratification","PIA",PIA_3_first_import,PIA_3_survey_first_import)
event_meta_data<-Event_data_cleaner("adobe","PIA 4: BHI Care Management Model","PIA",PIA_4_first_import,PIA_4_survey_first_import)
event_meta_data<-Event_data_cleaner("adobe","PIA 5: BHI Behaviorist Model","PIA",PIA_5_first_import,PIA_5_survey_first_import)
event_meta_data<-Event_data_cleaner("webx","Taking the Next Step: Year 2 Care Delivery Requirements","National Webinar",Taking_next_step_first_import,Taking_next_step_survey_first_import)
event_meta_data<-Event_data_cleaner("adobe","PIA 6: Using Data to Steer Care for High Risk Patients","PIA",PIA_6_first_import,PIA_6_survey_first_import)
event_meta_data<-Event_data_cleaner("adobe","PIA 7: Using Data to Steer High Volume High Cost Specialty Care","PIA",PIA_7_first_import,PIA_7_survey_first_import)
event_meta_data<-Event_data_cleaner("adobe","PIA 8: Agreeing how to Share the Care with Specialists","PIA",PIA_8_first_import,PIA_8_survey_first_import)
event_meta_data<-Event_data_cleaner("webx","Submitting your 2017 eCQM Data to CMS","National Webinar",submitting_eCQM_first_import,submitting_eCQM_survey_first_import)
event_meta_data<-Event_data_cleaner("adobe","PIA 9: Timely Exchange of Hospital and ED Data","PIA",PIA_9_first_import,PIA_9_survey_first_import)
event_meta_data<-Event_data_cleaner('webx',"Financial Reporting Office Hour","National Webinar",FR_OH_first_import,FR_OH_survey_first_import)
event_meta_data<-Event_data_cleaner('webx',"Care Delivery Orientation: Access and Continuity","Care Delivery Orientation Series",CDOS_AC_first_import,CDOS_AC_survey_first_import)
event_meta_data<-Event_data_cleaner('webx',"Care Delivery Orientation: Care Management","Care Delivery Orientation Series",CDOS_CM_first_import,CDOS_CM_survey_first_import)

#Seperate these 3 events into seperate dataframes for ease of use.

last_event<-as.data.frame(tail(event_meta_data,1))
previous_event<-as.data.frame(head(tail(event_meta_data,2),1))


comparison<-rbind(previous_event,last_event)

#finding events with same type
last_events_type<-event_meta_data[event_meta_data$`Event Type`==last_event$`Event Type`,]


melted_last_events_type<-melt(last_events_type,id.vars = 'Event_name')
melted_last_events_type<-melted_last_events_type[complete.cases(melted_last_events_type),]
event_names<-(as.list.data.frame(melted_last_events_type[1:(length(melted_last_events_type$Event_name)/25),1]))
sorted_event_names<-factor(event_names)
melted_last_events_type$Event_name<-factor(melted_last_events_type$Event_name,levels = sorted_event_names)

previous_event_same_type<-as.data.frame(head(tail(last_events_type,2),1))

comparison_same_type<-rbind(previous_event_same_type,last_event)

comparison_same_type$percentage_practices<-(as.numeric(comparison_same_type$Practice_attendees)/as.numeric(comparison_same_type$Attendance))

#averages and differences for same types of events
average_attendance_type<-mean(as.numeric(last_events_type$Attendance), na.rm=TRUE)

average_survey_response_rate_type<-mean(as.numeric(last_events_type$Survey_response_rate), na.rm=TRUE)

average_practices_type<-mean(as.numeric(last_events_type$Total_practices), na.rm=TRUE)

dif_attendance_type<-as.numeric(last_event$Attendance)-average_attendance_type

dif_survey_response_rate<-as.numeric(last_event$Survey_response_rate)-average_survey_response_rate_type

dif_practices<-as.numeric(last_event$Total_practices)-average_practices_type


##variables for our inline text

attendance_word<-ifelse(dif_attendance_type>0,"higher",ifelse(dif_attendance_type<0,"lower","same"))

survey_response_rate_word<-ifelse(dif_survey_response_rate>0,"higher",ifelse(dif_survey_response_rate<0,"lower","same"))

practices_word<-ifelse(dif_practices>0,"higher",ifelse(dif_practices<0,"lower","same"))



##Last Event Mapper

adobe_map_columns<-c(7,18,20,22,24)
adobe_map_names<-c("Attended","Type","ID","Region","zip")

webx_map_columns<-c(10,39,43,41,51)
webx_map_names<-adobe_map_names

map_cleaner<-function(type,imported_data){
  if(type=="adobe"){
    cleaned_data<-imported_data[,adobe_map_columns]
    colnames(cleaned_data)<-adobe_map_names
    cleaned_data<-cleaned_data[cleaned_data$Type=="Practice",]
  }else if(type=="webx"){
    cleaned_data<-imported_data[,webx_map_columns]
    colnames(cleaned_data)<-webx_map_names
    cleaned_data<-cleaned_data[cleaned_data$Type=="Primary care clinic",]
  }
  
  cleaned_data<-as.data.frame(cleaned_data)
  cleaned_data<-cleaned_data[cleaned_data$Attended=="Attended",]
  cleaned_data$zip<-clean.zipcodes(cleaned_data$zip)
  data("zipcode")
  cleaned_data<-left_join(cleaned_data,zipcode,by="zip")
  #So by doing a left join we have zip/state/city/lat/long
  
  
  return(cleaned_data)
}
state_shapes<-invisible(readOGR("cb_2016_us_state_500k.shp",layer = "cb_2016_us_state_500k", GDAL1_integer64_policy = TRUE))





```
<div class="intro">
##Intro

This is a (mostly) automated post-event report that tells a story with our data, and compares to other recent and similar events so that everything we present to the client is viewed in context. It will also help us benchmark our performances in Program Year 2 as we look to build upon the success that we experienced during the first year of CPC+.


## Last Event

This section looks at `r last_event$Event_name` which took place on `r as.Date.POSIXct(as.numeric(last_event$Date))`. It had <strong>`r last_event$Attendance` attendees </strong>  with `r round(as.numeric(last_event$Attendance_rate)*100,digits=1) `% of registrants attending. 


There were <strong>`r sum(as.numeric(last_event$Positive_VUT),as.numeric(last_event$Negative_VUT),as.numeric(last_event$Neutral_VUT))` respondents </strong> to the survey. This first graph shows the attendance and survey response rates.

</div>

###Attendance and Survey Response Rates


<div class="gauge">
```{r,echo = FALSE}
#gauge(round(as.numeric(last_event$Survey_response_rate)*100,digits=1),min = 0,max = 100,label = 'Survey Response Rate',symbol = '%')

source('gg_gauge.R')
attendance_gauge<-gg.gauge(round(as.numeric(last_event$Attendance_rate)*100,digits=1),'% Attendance',breaks = c(0,20,50,100))

survey_gauge<-gg.gauge(round(as.numeric(last_event$Survey_response_rate)*100,digits = 1),'% Survey Response',breaks = c(0,20,50,100))

grid.newpage()

grid.draw(grobTree(rectGrob(gp=gpar(fill="#E8E8E8")),arrangeGrob(attendance_gauge,survey_gauge,ncol = 2)))


```
</div>

###Survey Responses
This graph shows the survey responses to the Valuable use of time (VUT) and I Will Take Action (TA) questions on the survey.
```{r, echo= FALSE}
melted_last_event<-melt(last_event,id.vars = "Event_name")
survey_colors<-c("darkgreen","darkgoldenrod2","darkred","darkgreen","darkgoldenrod2","darkred")
graphing_melted<-melted_last_event[20:25,]
graphing_melted$value_numeric<-as.numeric(graphing_melted$value)
survey_barplot<-ggplot(graphing_melted,aes(variable,value_numeric,fill=variable))+geom_bar(stat = 'identity')+scale_fill_manual(values = survey_colors)+theme(plot.background = element_rect(fill = "#328CC1"),legend.background = element_rect(fill = "#328CC1"))
survey_barplot

```

<div class= "state_map">
  <div class="center">
###State Representation of Attending Practices
```{r, echo=FALSE, message=FALSE, warning=FALSE}
event_map_data<-map_cleaner("webx",CDOS_CM_first_import)
state_count<-table(event_map_data$state)
state_shapes$COUNT<-state_count[as.character(state_shapes$STUSPS)]
state_shapes$COUNT<-ifelse(is.na(state_shapes$COUNT),0,state_shapes$COUNT)
bins<-c(0,.5,.75,1,3,5,7,9,11,13,15,20,25,30,50,Inf)
pal_fil <- invisible(colorBin("YlOrRd", domain = state_shapes$COUNT,bins = bins))
practice_map<-leaflet(state_shapes)%>%
  setView(-80,37.8,3.25)%>%
  addPolygons(color="#4444444",fillColor = ~pal_fil(COUNT),weight = 2, opacity =1, fillOpacity = .8,highlight=
                highlightOptions(weight = 5, bringToFront = TRUE),label=paste(state_shapes$STUSPS,state_count[as.character(state_shapes$STUSPS)]))
practice_map





```
  </div>
  
  <div class= "sidebar">



```{r,echo=FALSE,message=FALSE}
regions_table<-as.data.frame(matrix(nrow = 19, ncol = 1))
colnames(regions_table)<-c("Region")
regions_table$Region<-c("AR","CO","HI","KS","MO","LA","MI","MT","NE","NJ","NY","ND","OH","KY","OK","OR","PA","RI","TN")
regions_table$Region<-as.character(regions_table$Region)
state_shapes_table<-as.data.frame(state_shapes[state_shapes$COUNT!=0,]$COUNT)
state_shapes_table$Region<-rownames(state_shapes_table)
colnames(state_shapes_table)<-c("State Count","Region")

state_shapes_table<-left_join(regions_table,state_shapes_table)
state_shapes_table$`State Count`<-ifelse(is.na(state_shapes_table$`State Count`),0,state_shapes_table$`State Count`)

final_regions_list<-c("AR","CO","HI","MO","LA","MI","MT","NE","NJ","NY","ND","OH","OK","OR","PA","RI","TN")
#Combining KS and MO
state_shapes_table[5,2]=state_shapes_table[5,2]+state_shapes_table[4,2]
#Combining KY and OH
state_shapes_table[13,2]=state_shapes_table[13,2]+state_shapes_table[14,2]
state_shapes_table<-subset(state_shapes_table, Region %in% final_regions_list)
kable(state_shapes_table,caption="Attendance by Region")




```

 </div>
</div>



<div class='attendees'>

###Role Representation of Attendees

This table gives a breakdown of Attendees by role.
```{r,echo= FALSE,results= 'asis'}
table_melted<-melted_last_event[6:16,2:3]
table_melted$value<-as.numeric(table_melted$value)
colnames(table_melted)<-c("Role","Number of Attendees")
#table_melted$variable<-sub("_"," ", table_melted$variable)
kable(table_melted,caption = "Attendance by Role",row.names=FALSE)

```

</div>

<div class="2018_starters">

###2018 Starters Representation
```{r, echo=FALSE}
checkboxInput('roundtwo_analysis',"Include 2018 Starters Breakdown?",value = FALSE)

source('Roundtwo_analysis.R')
R2_data<-Roundtwo_analysis(CDOS_CM_first_import,'webx')

reactive(
if(input$roundtwo_analysis==TRUE){
  print(R2_data)
}else{
  print("2018 analysis was not selected")
}
)




```
</div>

<div class= "Same__type">
##Same Type Comparison

This event had a `r attendance_word` attendance than the average attendance for this type of event and a `r practices_word` number of practices attend compared to the average. For the survey, it had a `r survey_response_rate_word` rate of response compared to other similar type events.

These graphs compare the last event to all of the other events of the same type.

###Attendance and Attendance Rate vs all Other Events

```{r, echo=FALSE}

attendance_barplot<-ggplot(melted_last_events_type[melted_last_events_type$variable=='Attendance',],aes(x=variable,y=as.numeric(value),fill=Event_name))+geom_bar(stat='identity', position = 'dodge')+geom_hline(yintercept = mean(as.numeric(melted_last_events_type[melted_last_events_type$variable=='Attendance',]$value)),linetype=2)+annotate("text",x = 0, y= mean(as.numeric(melted_last_events_type[melted_last_events_type$variable=='Attendance',]$value)),vjust= 2,hjust =-.1,label="Average Attendance")+xlab('Event')+ylab('Number of Attendees')

attendance_barplot<-attendance_barplot+theme(axis.text.x = element_blank(),plot.background =element_rect(fill = "#328CC1"),legend.background = element_rect(fill = "#328CC1"))


attendance_rate_barplot<-ggplot(melted_last_events_type[melted_last_events_type$variable=='Attendance_rate',],aes(x=variable,y=as.numeric(value),fill=Event_name))+geom_bar(stat='identity', position = 'dodge')+geom_hline(yintercept = mean(as.numeric(melted_last_events_type[melted_last_events_type$variable=='Attendance_rate',]$value)),linetype=2)+annotate("text",x = 0, y= mean(as.numeric(melted_last_events_type[melted_last_events_type$variable=='Attendance_rate',]$value)),vjust= 2,hjust =-.1,label="Average Attendance Rate")+xlab('Event')+ylab('Attendance Rate')

attendance_rate_barplot<-attendance_rate_barplot+theme(axis.text.x = element_blank(),plot.background = element_rect(fill = "#328CC1"),legend.background = element_rect(fill = "#328CC1"))

##Room for another graph or two-- get team feedback

source('multiplot.R')
multiplot(attendance_barplot,attendance_rate_barplot)


```

</div>

<div class="previous_event">

##Previous Event Comparision

This section gives a more in-depth breakdown between `r last_event$Event_name` and the previous `r last_event$'Event Type' `, which was titled `r comparison_same_type$Event_name[1] ` and took place on `r as.Date.POSIXct(as.numeric(comparison_same_type$Date[1])) `.


This first plow shows the distribution of attending roles for each event, while the second shows the comparison between positive responses to the survey question "Attending this session was a valuable use of my time".

###Survey and Role Comparison to Last `r last_event$'Event Type' `
```{r, echo=FALSE}
comparison_same_type$Survey_respondents<-(as.numeric(comparison_same_type$Positive_VUT)+as.numeric(comparison_same_type$Neutral_VUT)+as.numeric(comparison_same_type$Negative_VUT))
comparison_same_type$Positive_percentage<-round(as.numeric(comparison_same_type$Positive_VUT)/(comparison_same_type$Survey_respondents),2)
comparison_same_type$Neutral_percentage<-round(as.numeric(comparison_same_type$Neutral_VUT)/(comparison_same_type$Survey_respondents),2)
comparison_same_type$Negative_percentage<-round(as.numeric(comparison_same_type$Negative_VUT)/(comparison_same_type$Survey_respondents),2)

melted_comparison<-melt(comparison_same_type,id.vars="Event_name")


role_barplot<-ggplot(melted_comparison[11:32,],aes(x=variable,y=as.numeric(value),fill=Event_name))+geom_bar(stat = 'identity',position = 'dodge')+theme(axis.text.x = element_text(angle = 90, hjust = 1),plot.background = element_rect(fill = "#328CC1"),legend.background = element_rect(fill = "#328CC1"))+scale_y_continuous(breaks = seq(0,60,5))+xlab('Attendee Role')+ylab('Number attending')

#role_barplot

survey_percents_1<-ggplot(melted_comparison[seq(55,59,2),],aes(x='',y=as.numeric(value),fill=variable,label=as.numeric(value)))+geom_bar(width=1,stat = 'identity')+geom_text()
survey_percents_1<-survey_percents_1+coord_polar('y', start = 0)+ggtitle(paste('Survey Responses for ',melted_comparison[55,]$Event_name))+theme(axis.text.x=element_blank(),axis.title.x = element_blank(),axis.title.y=element_blank(),plot.background = element_rect(fill = "#328CC1"),legend.background = element_rect(fill = "#328CC1"))


survey_percents_2<-ggplot(melted_comparison[seq(56,60,2),],aes(x='',y=as.numeric(value),fill=variable,label=as.numeric(value)))+geom_bar(width=1,stat = 'identity')+geom_text()
survey_percents_2<-survey_percents_2+coord_polar('y', start = 0)+ggtitle(paste('Survey Responses for ',melted_comparison[56,]$Event_name))+theme(axis.text.x=element_blank(),axis.title.x = element_blank(),axis.title.y=element_blank(),plot.background = element_rect(fill = "#328CC1"),legend.background = element_rect(fill = "#328CC1"))



source('multiplot.R')
role_barplot
multiplot(survey_percents_1,survey_percents_2)

```

</div>



