---
title: "Post_Event_Report"
author: "Sam Gottuso"
date: "December 7, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(ggplot2)
library(dplyr)
library(knitr)
library(rmarkdown)
library(readr)
library(reshape2)


##Load in functions necessary for creating DFs

#Figures out the mode of dates to determine what the correct date is
Mode_manual <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}


#standardization of which columns/names of columns
column_names_adobe<-c("First_name","Last_name","Email","Status","Login","Logoff","Duration","Role","Role_other","Organization_name","ID","Region","Zip")
  
column_numbers_adobe<-c(3,4,5,7,8,9,10,12,13,16,18,21,23)

column_names_webx<-column_names_adobe
column_numbers_webx<-c(1,2,3,10,11,12,19,33,34,37,43,41,51)

column_numbers_sm<-seq(10,18)
column_names_sm<-c("Track","Reported_role","Reported_role_other","Valuable_use_time","Connect_others","Take_action","Enhanced_knowledge","Suggestions","Technical_difficulties")

#This is a change


##Test data


#PIA2

PIA_2_first_import<-read_excel(path='C:/Users/583185/Desktop/data_science/post_event_reporting/PIA2_analysis.xlsx',sheet = 2)


PIA_2_survey_first_import<-read_excel(path='C:/Users/583185/Desktop/data_science/post_event_reporting/PIA_2_survey.xlsx',sheet = 1)



#ecqm_HIT_Review

eCQM_HIT_first_import<-read_excel(path='C:/Users/583185/Desktop/data_science/post_event_reporting/eCQM_HIT_analysis.xlsx',sheet = 1)

ecqm_HIT_survey<-read_excel(path='C:/Users/583185/Desktop/data_science/post_event_reporting/eCQM_HIT_Survey.xlsx', sheet = 1)




##Automatically Clean and Split out necessary data 

event_meta_data<-data.frame(matrix(NA,ncol=26))
colnames(event_meta_data)<-c("Date","Event_name","Event Type","Attendance","Attendance_rate","Practice_attendees","Administration","Clinicians","Care_managers","Data_analyst","Project_managers","Project_director","Quality_improvement","CMS","Contractors","Payers","Vendors","Unique_practices","Total_practices","Survey_response_rate","Positive_VUT","Neutral_VUT","Negative_VUT","Positive_TA","Netural_TA","Negative_TA")

Event_data_cleaner<-function(type,event_name,event_type,imported_data,imported_survey_data){
  if(type=="adobe"){
    cleaned_data<-imported_data[,column_numbers_adobe]
    colnames(cleaned_data)<-column_names_adobe
  }else if(type=="webx"){
    cleaned_data<-imported_data[,column_numbers_webx]
    colnames(cleaned_data)<-column_names_webx
  }
  
  cleaned_data<-as.data.frame(cleaned_data)
  
  #Adding date
  date<-Mode_manual(na.omit(cleaned_data$Login))

  #Adding Attendance and attendance rate
  attendance<-(sum(cleaned_data$Status=="Attended",na.rm = TRUE))
  attendance_rate<-(attendance)/length(cleaned_data$Status)

  #Adding practice participants-- from attended only
  attended_df<-cleaned_data[(cleaned_data$Status=="Attended"),]
  admin<-sum(attended_df$Role=="Administration",na.rm = TRUE)
  drs<-sum(attended_df$Role=="Clinicians providing healthcare services within context of model",na.rm = TRUE)
  cm<-sum(attended_df$Role=="Care Manager",na.rm = TRUE)
  da<-sum(attended_df$Role=="Data Analysts",na.rm = TRUE)
  pm<-sum(attended_df$Role=="Project Manager/Coordinator",na.rm = TRUE)
  pd<-sum(attended_df$Role=="Project Director/Principal Investigator",na.rm = TRUE)
  qi<-sum(attended_df$Role=="Quality Improvement Director",na.rm = TRUE)
  PA<-sum(admin,drs,cm,da,pm,pd,qi)
  
  #Adding non-practice attendees
  cms<-sum(attended_df$Role=="CMS",na.rm = TRUE)
  cnt<-sum(attended_df$Role=="Contractor",na.rm = TRUE)
  pay<-sum(attended_df$Role_other=="Payer",na.rm = TRUE)
  ven<-sum(attended_df$Role_other=="Vendor",na.rm = TRUE)
  
  #Practices
  up=length(unique(attended_df$ID))
  tp=sum(attended_df$ID!="Not Available",na.rm = TRUE)
  
  
  ##Survey Stuff
  cleaned_data_survey<-imported_survey_data[,column_numbers_sm]
  colnames(cleaned_data_survey)<-column_names_sm
  
  cleaned_data_survey<-tail(cleaned_data_survey,-1)
  cleaned_data_survey<-cleaned_data_survey[rowSums(is.na(cleaned_data_survey))!=ncol(cleaned_data_survey),]
  
  cleaned_data_survey<-as.data.frame(cleaned_data_survey)
  
  srr<-(length(cleaned_data_survey$Track)/attendance)
  
  cleaned_data_survey$VUT<-parse_number(cleaned_data_survey$Valuable_use_time)
  cleaned_data_survey$TA<-parse_number(cleaned_data_survey$Take_action)
  
  p_vut<-sum(cleaned_data_survey$VUT==5)+sum(cleaned_data_survey$VUT==4)
  nu_vut<-sum(cleaned_data_survey$VUT==3)
  n_vut<-sum(cleaned_data_survey$VUT==2)+sum(cleaned_data_survey$VUT==1)
  
  p_TA<-sum(cleaned_data_survey$TA==5)+sum(cleaned_data_survey$TA==4)
  nu_TA<-sum(cleaned_data_survey$TA==3)
  n_TA<-sum(cleaned_data_survey$TA==2)+sum(cleaned_data_survey$TA==1)
  
  
  TD<-sum(cleaned_data_survey$Technical_difficulties=="Yes")
  
  

append_list<-c(date,event_name,event_type,attendance,attendance_rate,PA,admin,drs,cm,da,pm,pd,qi,cms,cnt,pay,ven,up,tp,srr,p_vut,nu_vut,n_vut,p_TA,nu_TA,n_TA,TD)

event_meta_data<-rbind(event_meta_data,append_list)

return(event_meta_data)
  
}

event_meta_data<-Event_data_cleaner("adobe","PIA2","PIA",PIA_2_first_import,PIA_2_survey_first_import)
event_meta_data<-Event_data_cleaner("webx","eCQM HIT Review","National Webinar",eCQM_HIT_first_import,ecqm_HIT_survey)

last_event<-tail(event_meta_data,1)
previous_event<-head(tail(event_meta_data,2),1)

```

##Intro/Just Last Event

This is a (mostly) automated post-event report that tells a story with our data, and compares to other recent and similar events so that everything we present to the client is viewed in context. It will also help us benchmark our performances in Program Year 2 as we look to build upon the success that we experienced during the first year of CPC+.

```{r, echo= FALSE}
melted_last_event<-melt(last_event,id.vars = "Event_name")
survey_colors<-c("green","yellow","red","green","yellow","red")
survey_barplot<-ggplot(melted_last_event[20:25,],aes(variable,value))+geom_bar(stat = 'identity',aes(fill=melted_last_event[20:25,]$value))+scale_fill_manual(values = survey_colors)
survey_barplot

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

##Previous Event Comparision



##Monthly Comparison


##Quarterly Comparison

##Similar Events comparison
